Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-18 paper/paper.tex
More tissue visualisation. Next up: figure of all surgical manips, but only expression 0.1

The `chemoaffinity only' model begins to encounter problems when we introduce
simulations of experimental manipulations. Fig\,\ref{f:chsurg} shows the
results of 6 simulated surgical manipulations. In row A, a patch of tectal
tissue has been cut out and rotated by a quarter turn. This is achieved in
simulation by rotating a square region of the tectal region

% Visualisation of ligand expression and gradients on the tectum for the
% graft-rotate 90 degrees simulated surgical manipulation
\begin{figure}
\includegraphics[width=\linewidth]{./images/Tissuevisb.png}
\caption{Visualisation of ligand expression and gradients on the tectum for the
graft-rotate 90 degrees simulated surgical manipulation}
\label{f:tvrot90}
\end{figure}

>>>>

The `chemoaffinity only' model begins to encounter problems when we introduce
simulations of experimental surgical manipulations. Simulated surgery is
performed by manipulating the maps shown in
Fig.\,\ref{f:ex}. Fig.\,\ref{f:trot90} shows the expression maps and the
resulting gradients that result from the surgical manipulation in which a
graft of the tectum is rotated by a quarter turn and replaced. We rotate an
8x8 square of the tectum and then recompute the gradients. As the expression
is discretized, we also discretize the gradient, with the gradient in
direction $x$ computed as the difference between the expression of the two
neighbouring elements divided by twice the element distance. As there are four
ligands expressed on the tectum, there are four pairs of gradient maps, all of
which are shown in Fig.\,\ref{f:trot90}.

% Visualisation of ligand expression and gradients on the tectum for the
% graft-rotate 90 degrees simulated surgical manipulation
% ./build/sim/agent/tissuevis configs/simpler/m_eE_G.json configs/simpler/e_tecrot90_fig4row1.json
%
\begin{figure}
\includegraphics[width=\linewidth]{./images/Tissuevisb.png}
\caption{Visualisation of ligand expression and gradients on the tectum for the
graft-rotate 90 degrees simulated surgical manipulation}
\label{f:trot90}
\end{figure}

Fig.\,\ref{f:tmanip} shows the tectal ligand expression for ligands $L_1$ and
$L_2$ for the five other surgical manipulations applied in this work. These
are a 180\degree rotation (Fig\,\ref{f:tmanip}A), a graft-swap manipulation
(Fig\,\ref{f:tmanip}B), ablation of half the retina  (Fig\,\ref{f:tmanip}C),
ablation of half the tectum (Fig\,\ref{f:tmanip}D) and a mismatch ablation in
which half of the retina is removed along with the half of the tectum to which
the remaining retina would project (Fig\,\ref{f:tmanip}E).

\begin{figure}
\includegraphics[width=\linewidth]{./images/TissueManips.png}
\caption{Visualisation of ligand expression and gradients on the tectum for the
other simulated surgical manipulations}
\label{f:tmanip}
\end{figure}

Fig\,\ref{f:chsurg} shows the
results of 6 simulated surgical manipulations. In row A, a patch of tectal
tissue has been cut out and rotated by a quarter turn. This is achieved in
simulation by rotating a square region of the tectal region.
